---
title: "Analysis of Superstore Furniture Sales Data"
author: "Yupawadee Galasong"
date: "2023-02-19"
output: html_document
bibliography: packages.bib
link-citations: true
nocite: '@*'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::write_bib(c("base", "tidyverse", "ggpubr","rstatix","stats"), "packages.bib")
library(tidyverse)
library(devtools)
library(ggpubr)
library(rstatix)
library(stats)
```

# Analyses to be performed

1.  Summary statistics such as mean, median and standard deviation
2.  Normality and Homogeneity of Variance check
3.  One-Way ANOVA
4.  Post-hoc test

# Introduction

The 'Superstore' dataset contains \~ 10,000 entries of sales data. The following information is recorded: order ID, order date, ship date, ship mode, customer information (name, address, segment), product information, sales, discount and profit. To begin the analysis, we import the dataset and reformat certain columns as needed.

```{r import}
Superstore <- read_csv("../Data/Superstore.csv", 
    col_types = cols(`Order Date` = col_date(format = "%m/%d/%Y"), 
        `Ship Date` = col_date(format = "%m/%d/%Y")))
head(Superstore)
```

# Calculating summary statistics

We might want to know the average sales and profits the store gained from different consumer segment. Using tidyverse [@R-tidyverse] meta-package allows us to perform routine data science tasks such as computing summary statistics and grouping data frame.

```{r summary stats1}
#Average sales and profit grouped by customer segment and region
Superstore %>%
  group_by(Segment) %>%
  summarise(
          count = n(),
          avg_sales = mean(Sales),
          avg_profit = mean(Profit)
            )
```

The average sales and profit are quite similar. It is interesting that home office segment has lowest avaergae profit despite having the highest sales in the record. Now let's look at the maximum and minimum sales & profits generated by each region.

```{r summary stats2}
#Maximum sales and profits grouped by region
Superstore %>%
  group_by(Region) %>%
  summarise(
          count = n(),
          max_sales = max(Sales),
          min_sales = min(Sales),
          max_profit = max(Profit),
          min_profit = min(Profit)
            )
```

Alternatively, we can explore the median sales and profit generated from different product subcategory.

```{r summary stats3}
#Median sales grouped by product sub-category
Superstore %>%
  group_by(`Sub-Category`) %>%
  summarise(
          count = n(),
          median_sales = median(Sales),
          median_profit = median(Profit)
            )

```

# Visualizing sales data in the furniture category

We might want to know if sales and profit are normally distributed. We can visualize these data using histograms.

```{r histogram_untransformed}
ggplot(data = filter(Superstore, Category == "Furniture"), aes(x = Sales, fill = Segment)) + geom_histogram(binwidth = 200) + scale_fill_brewer(palette = "Pastel1") + labs(title = "Distribution of Sales in the Furniture Category")
```

The data looks left-skewed. We could apply log transformation to the sales data. We can also see that the distribution within each consumer segment is similar. The only difference is the sales volume.

```{r histogram_log_transformed, message=FALSE}
ggplot(data = filter(Superstore, Category == "Furniture"), aes(x = log(Sales), fill = Segment)) + geom_histogram(binwidth = 1) + scale_fill_brewer(palette = "Pastel1") + labs(title = "Distribution of Sales in the Furniture Category")

#Save the plot
ggsave("Histogram of Furniture Sales.png")
```

# Statistical comparison of sales data in the furniture category

Let's create a new data frame by subsetting the initial Superstore dataset.

```{r subset data}
Furniture = subset(Superstore, Category == "Furniture")
```

We want to know if which product subcategory within the furniture category generated significant sales. To get a glimpse of how the subcategories stacks up against one another, we can visualize it with side-by-side boxplots.

```{r boxplot}
ggplot(data = Furniture, aes(x = `Sub-Category`, y = log(Sales),fill = `Sub-Category`))+ geom_violin()+labs(title = "Furniture Sales by Subcategories ")+scale_fill_brewer(palette = "Pastel2")
```

## Checking normality assumption

Before performing Analysis of Variance (ANOVA), we should make sure that the data meets certain assumptions, one of which is the normality assumption. Normality is generally visualized using QQplot.

```{r}
#Add a new column of log-transformed sales to the Furniture dataframe because ggqqplot cannot accept log(Sales) as input.
Furniture$log_Sales = log(Furniture$Sales)

#QQ plot
ggqqplot(Furniture, "log_Sales", facet.by = "Sub-Category")
```

All the points fall approximately along the reference line, for each cell. So we can assume normality of the log-transformed sales data.

## Checking the assumption of homogeneity of variances

Levene's test can be used to check the homogeneity of variances; i.e. if variances are equal.

```{r Homogeneity of Variances, warning=FALSE}
#Displaying results in a tibble
Furniture %>% levene_test(log_Sales ~ `Sub-Category`)

```

The p-value of the Levene's test is way below 0.05, which tells us that the variances are significantly different among product subcategories! We should not be performing a typical ANOVA because the homogeneity of variance assumption is not met. However, we can st will compute run a specific kind of ANOVA that has Welch statistic. This test does not require the assumption of equal variances [@R-rstatix].

## Welch One-Way ANOVA Test

```{r}
#Convert Sub-Category to a factor
Furniture$`Sub-Category` <- as.factor(Furniture$`Sub-Category`)

#Run the test
Furniture %>% welch_anova_test(log_Sales~`Sub-Category`)
```

One-way ANOVA with Welch test suggests that at least one of the subcategories has a significantly different sales compared to others. We will proceed with a post-hoc test to determine the significant sub-category. There are multiple post-hoc test available depending on the assumptions about the data. We know from the Levene's test that our furniture sales data have unequal variances. Next, we need to find out if the sample sizes among the sub-categories are equal.

```{r count}
#Another summary statistics of furniture sub-category
Furniture %>%
  group_by(`Sub-Category`) %>%
  summarise(
          count = n(),
          mean_sales = mean(Sales),
          SD_sales = sd(Sales))
```

Since the sample size is also unequal, the following post-hoc tests are appropriate: Dunette's test, Games-Howell test and Tamhane test. Let's use Games-Howell test.

```{r Games Howell}

Furniture %>% rename("SubCategory" = "Sub-Category") %>% games_howell_test(log_Sales~SubCategory)

```

Games-Howell test shows that all pairwise comparisons, except for Bookcases Vs Chairs, yield significant results. To visualize the statistical significance on a plot, we have to save the test results to a new data frame.

```{r, warning=FALSE}
# Welch One way ANOVA test

welch.aov <- Furniture %>% welch_anova_test(log_Sales~`Sub-Category`)

# Pairwise comparisons (Games-Howell)
pwc <- Furniture %>% rename("SubCategory" = "Sub-Category") %>% games_howell_test(log_Sales~SubCategory)

# Visualization: box plots with p-values
pwc <- pwc %>% add_y_position(step.increase = 1)
ggboxplot(Furniture %>% rename("SubCategory" = "Sub-Category") , 
          x = "SubCategory", y = "log_Sales", fill = "SubCategory")+
  scale_fill_brewer(palette = "Pastel2") +
  stat_pvalue_manual(pwc, hide.ns = TRUE, label = "p.adj.signif") + 
  labs(
    title = "Furniture Sales are Significantly Different Among Subcategories", 
    subtitle = get_test_label(welch.aov, detailed = TRUE),
    caption = get_pwc_label(pwc)) + theme(legend.position = "none")
```
Finally, let's try fitting a linear model on the furniture data.
We will use lm() function to fit a model. We can also include interaction terms, for example, Segment*Region to see if those predictors together can significantly affects the outcome.
```{r}

lm.fit <- lm(log_Sales~`Sub-Category`+Segment + Region+ Quantity+Discount+`Ship Mode`+Segment:Region, data = Furniture)
summary(lm.fit)
```
Based on the summary of the model, it seems that subcategories 'chairs','Furnishings' and 'Tables' are significant predictors of furniture sales. Quantity and Discount are significant too. This makes sense because we can expect that higher discount generally means lower sales. While Segment and Region on their own are not that significant, fitting the an interaction term of those two predictors reveals that corporate consumers on in the West is a high-spending segment. This could be a useful information in business or marketing-related decision making. 

The model summary also shows that the R-squared value is 0.64, meaning that only 64% of the variances in the sales data can be explained by the list of predictors we chose for this model. 

# Conclusion
We explored the Superstore sales data with the emphasis on furniture sales data. One-way ANOVA test with Welch statistic shows that the furniture subcategories have significantly different sales. Finally, we fit a linear model with an interaction term and obtained a model with an R-squared value of 0.64.
```{r}
devtools::session_info()
```
# Bibliography