---
title: "Analysis of Superstore Sales Data"
author: "Yupawadee Galasong"
date: "2023-02-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
```

# Importing the Dataset

The 'Superstore' dataset contains \~ 10,000 entries of sales data. The following information is recorded: order ID, order date, ship date, ship mode, customer information (name, address, segment), product information, sales, discount and profit. To begin the analysis, we import the dataset and reformat certain columns as needed.

```{r import}
Superstore <- read_csv("../Data/Superstore.csv", 
    col_types = cols(`Order Date` = col_date(format = "%m/%d/%Y"), 
        `Ship Date` = col_date(format = "%m/%d/%Y")))
head(Superstore)
```

# Calculating summary statistics

We might want to know the average sales and profits the store gained from different consumer segment.

```{r summary stats1}
#Average sales and profit grouped by customer segment and region
Superstore %>%
  group_by(Segment) %>%
  summarise(
          count = n(),
          avg_sales = mean(Sales),
          avg_profit = mean(Profit)
            )
```

```{r summary stats2}
#Maximum sales and profits grouped by region
Superstore %>%
  group_by(Region) %>%
  summarise(
          count = n(),
          max_sales = max(Sales),
          min_sales = min(Sales),
          max_profit = max(Profit),
          min_profit = min(Profit)
            )
```

```{r summary stats3}
#Median sales grouped by product sub-category
Superstore %>%
  group_by(`Sub-Category`) %>%
  summarise(
          count = n(),
          median_sales = median(Sales),
          median_profit = median(Profit)
            )
```
